---
title: "Testing the input and output of Area"
author: "Judith Neve"
date: "20/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(CTmeta)
library(vars)
```

This document tests what can be used as input and output for the function Area. Each argument is examined in turn, and at the end some additional checks are done to verify plots can be made for different configurations of the model.

Where the function runs, the output is compared to the expected output.

After every attempt to "break" the function, a diagnostic is written as a comment in the code chunk, and the code chunk is followed by a "to do" list to indicate what needs to be specified/improved/changed in the function documentation or the function itself.

Original example:

```{r}
DeltaT <- 1
Phi <- myPhi[1:2, 1:2]
Drift <- myDrift
data <- myData
out_VAR <- VAR(data, p = 1)
```

```{r}
res.phi <- Area(DeltaT = DeltaT, Phi = Phi)
res.drift <- Area(DeltaT, Drift = Drift)
res.VAR <- Area(DeltaT, out_VAR)
```

```{r}
res.drift$Area == res.phi$Area
res.drift$Area_range == res.phi$Area_range

res.drift$Area == res.VAR$Area
res.drift$Area_range == res.VAR$Area_range
```



# DeltaT

## DeltaT a vector with repeating numbers

```{r}
DeltaT.break <- rep(1, 3)

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi) %>%
  try()
```

The error works fine.

## DeltaT a vector with different numbers

Already covered by the previous error.

## DeltaT a matrix

Already covered by the previous error.

## DeltaT = 0

```{r}
DeltaT.break <- 0

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi) %>%
  try()
```

To do:

- the problem is in CTMparam

## DeltaT a decimal

```{r}
DeltaT.break <- 1.5

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi)
res.phi.break
```

## DeltaT a small decimal

```{r}
DeltaT.break <- 0.01

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi)
res.phi.break
```

## Negative DeltaT

```{r}
DeltaT.break <- -1

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi)
res.phi.break

res.phi.break$Area == res.phi$Area
res.phi.break$Area_range == res.phi$Area_range
```

To do:

- the problem is meant to be DeltaT here, not Drift; the message should be changed, but the solutions are the same

## DeltaT = Inf

```{r}
DeltaT.break <- Inf

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi) %>%
  try()
```

To do:

- add an error for DeltaT = Inf

## DeltaT a large number

```{r}
DeltaT.break <- 10000

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi)
res.phi.break
```

## DeltaT = -Inf

```{r}
DeltaT.break <- -Inf

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi) %>%
  try()
```

To do:

- add an error for DeltaT = -Inf

## DeltaT a character

```{r}
DeltaT.break <- "text"

res.phi.break <- Area(DeltaT = DeltaT.break,
                      Phi = Phi) %>%
  try()
```

To do:

- add an error for DeltaT as text




# Phi

## Not square matrix

```{r}
Phi.break <- cbind(Phi, c(1, 1))

res.phi.break <- Area(DeltaT = DeltaT,
                      Phi = Phi.break) %>%
  try()
```

The error is clear.

## Phi with NAs

```{r}
Phi.break <- Phi
Phi.break[1,2] <- NA

res.phi.break <- Area(DeltaT = DeltaT,
                      Phi = Phi.break) %>%
  try()
```

To do:

- add an error if Phi has NAs

## Phi with non-numbers

```{r}
Phi.break <- Phi
Phi.break[1,2] <- "text"

res.phi.break <- Area(DeltaT = DeltaT,
                      Phi = Phi.break) %>%
  try()
```

To do:

- add an error if Phi has non-numerical values




# Drift

## Both Phi and Drift

```{r}
res.phi.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      Drift = Drift)

res.phi.break

res.phi.break$Area == res.phi$Area
res.phi.break$Area_range == res.phi$Area_range
```

To do:

- add a warning if both Phi and Drift are specified

## Not square matrix

```{r}
Drift.break <- cbind(Drift, c(1, 1))

res.drift.break <- Area(DeltaT = DeltaT,
                      Drift = Drift.break) %>%
  try()
```

The error is clear.

## Drift with NAs

```{r}
Drift.break <- Drift
Drift.break[1,2] <- NA

res.drift.break <- Area(DeltaT = DeltaT,
                      Drift = Drift.break) %>%
  try()
```

To do:

- add an error if Drift has NAs

## Drift with non-numbers

```{r}
Drift.break <- Drift
Drift.break[1,2] <- "text"

res.drift.break <- Area(DeltaT = DeltaT,
                      Drift = Drift.break) %>%
  try()
```

To do:

- add an error if Drift has non-numerical values



# t_min

## Specified

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = 2)

res.tmin.break$Area == res.phi$Area
res.tmin.break$Area_range == res.phi$Area_range
```

Only Area_range changes, as expected.

## Negative

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = -3)

res.tmin.break$Area == res.phi$Area
res.tmin.break$Area_range == res.phi$Area_range
```

Area_range changes.

To do:

- ask Rebecca if this is normal.

## Decimal

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = 2.5)
res.tmin.break

res.tmin.break$Area == res.phi$Area
res.tmin.break$Area_range == res.phi$Area_range
```

This works well.

## Inf

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = Inf) %>%
  try()
```

To do:

- add an error

## -Inf

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = -Inf) %>%
  try()
```

To do:

- add an error

## Character

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = "text") %>%
  try()
```

To do:

- add an error

## Vector

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = c(1, 2))
res.tmin.break

res.tmin.break$Area == res.phi$Area
res.tmin.break$Area_range == res.phi$Area_range
```

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = c(0, 2))
res.tmin.break

res.tmin.break$Area == res.phi$Area
res.tmin.break$Area_range == res.phi$Area_range
```

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = c(2, 0))
res.tmin.break

res.tmin.break$Area == res.phi$Area
res.tmin.break$Area_range == res.phi$Area_range
```

```{r}
res.tmin.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = c(0, 0))
res.tmin.break

res.tmin.break$Area == res.phi$Area
res.tmin.break$Area_range == res.phi$Area_range
```

To do:

- add an error if t_min is not a scalar



# t_max

## Specified

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = 2)

res.tmax.break$Area == res.phi$Area
res.tmax.break$Area_range == res.phi$Area_range
```

As expected.

## Smaller than t_min

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = 3,
                      t_max = 2)
res.tmax.break

res.tmax.break$Area == res.phi$Area
```

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = 3,
                      t_max = 2)

res.range <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = 2,
                      t_max = 3)

res.tmax.break$Area == res.range$Area
res.tmax.break$Area_range == -(res.range$Area_range)
```

To do:

- add a warning saying t_max is larger than t_min

## t_max = t_min

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_min = 3,
                      t_max = 3)
res.tmax.break

res.tmax.break$Area == res.phi$Area
```

Works.

## Decimal

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = 3.5)
res.tmax.break

res.tmax.break$Area == res.phi$Area
```

Works.

## Negative

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = -3.5)
res.tmax.break

res.tmax.break$Area == res.phi$Area
```

Works.

## Inf

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = Inf)
res.tmax.break

res.tmax.break$Area == res.phi$Area
res.tmax.break$Area_range == res.phi$Area_range
```

## Character

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = "text") %>%
  try()
```

To do:

- add an error for text

## Vector

```{r}
res.tmax.1 <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = 1)

res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = c(1, 2))
res.tmax.break

res.tmax.break$Area == res.phi$Area
res.tmax.break$Area_range == res.tmax.1$Area_range
```

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = c(0, 2))
res.tmax.break

res.tmax.break$Area == res.phi$Area
res.tmax.break$Area_range == res.phi$Area_range
```

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = c(2, 0))
res.tmax.break

res.tmax.break$Area == res.phi$Area
res.tmax.break$Area_range == res.phi$Area_range
```

```{r}
res.tmax.break <- Area(DeltaT = DeltaT,
                      Phi = Phi,
                      t_max = c(0, 0))
res.tmax.break

res.tmax.break$Area == res.phi$Area
res.tmax.break$Area_range == res.phi$Area_range
```

To do:

- add an error if t_max is not a scalar


