---
title: "Testing the input and output of Area"
author: "Judith Neve"
date: "20/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(CTmeta)
```

This document tests what can be used as input and output for the function Area. Each argument is examined in turn, and at the end some additional checks are done to verify plots can be made for different configurations of the model.

Where the function runs, the output is compared to the expected output.

After every attempt to "break" the function, a diagnostic is written as a comment in the code chunk, and the code chunk is followed by a "to do" list to indicate what needs to be specified/improved/changed in the function documentation or the function itself.

Original example:

```{r}
Drift <- myDrift
q <- dim(Drift)[1]
Sigma <- diag(q)
Gamma <- Gamma.fromCTM(Drift, Sigma)

sig <- ChecksCTM(Drift, Sigma)
gam <- ChecksCTM(Drift, Gamma = Gamma)
```




# Drift

## Drift with too many rows

```{r}
Drift.broken <- rbind(Drift, c(1, 1))

ChecksCTM(Drift.broken, Sigma) %>% try()
```

Understandable error message.


## Drift with too many columns

```{r}
Drift.broken <- cbind(Drift, c(1, 1))

ChecksCTM(Drift.broken, Sigma) %>% try()
```

Understandable error message.


## Drift with NAs

```{r}
Drift.broken <- Drift
Drift.broken[1,2] <- NA

ChecksCTM(Drift.broken, Sigma) %>% try()
```

Added an error for missing values in Drift.


## No Drift, only Sigma and Gamma

```{r}
ChecksCTM(Sigma = Sigma, Gamma = Gamma) %>% try()
```


## All three

```{r}
ChecksCTM(Drift, Sigma, Gamma)
```

## All three, but non-compatible

```{r}
Drift.broken <- Drift
Drift.broken[1,1] <- -1.75

ChecksCTM(Drift.broken, Sigma, Gamma)
```

```{r}
Sigma.broken <- Sigma
Sigma.broken[2,1] <- -1.75

ChecksCTM(Drift, Sigma.broken, Gamma)
```

```{r}
Gamma.broken <- Gamma
Gamma.broken[2,1] <- -1.75

ChecksCTM(Drift, Sigma, Gamma.broken)
```

Added a check that they are all compatible.


## Only Drift

```{r}
ChecksCTM(Drift) %>% try()
```

Clear error.


## Drift with non-numerical values

```{r}
Drift.broken <- Drift
Drift.broken[1,2] <- "text"

ChecksCTM(Drift.broken, Sigma) %>% try()
```

Added an error.

## Drift with positive eigenvalues

```{r}
Drift.broken <- matrix(c(2, -1, -1, 2), nrow = 2)

pos.eig <- ChecksCTM(Drift.broken, Sigma)
pos.eig$error
```

Problems:
- prints some stuff that is not saved (in "cat" functions)
- there are no returns to line in lists so \n is always visible


## Drift with complex eigenvalues

```{r}
Drift.broken <- matrix(c(1/2, -1/2, 3/4, 5/4), nrow = 2, byrow = TRUE)

complex.eig <- ChecksCTM(Drift.broken, Sigma)
complex.eig$error
```

## Drift with complex eigenvectors

```{r}
Drift.broken <- matrix(c(1/2, -0.6, 3/4, 1.1), nrow = 2, byrow = TRUE)

complex.eig <- ChecksCTM(Drift.broken, Sigma)
complex.eig$error
```

## Drift with positive and complex eigenvalues

Assuming this works ok.



# Sigma

## More rows

```{r}
Sigma.broken <- rbind(Sigma, c(1, 1))

ChecksCTM(Drift, Sigma.broken) %>% try()
```

## More columns

```{r}
Sigma.broken <- cbind(Sigma, c(1, 1))

ChecksCTM(Drift, Sigma.broken) %>% try()
```

## NAs

```{r}
Sigma.broken <- Sigma
Sigma.broken[1,1] <- NA

ChecksCTM(Drift, Sigma.broken) %>% try()
```

Added an error for NAs in Sigma.

## Non-numbers

```{r}
Sigma.broken <- Sigma
Sigma.broken[1,1] <- "text"

ChecksCTM(Drift, Sigma.broken) %>% try()
```

## Not diagonal

```{r}
Sigma.broken <- Sigma
Sigma.broken[1,2] <- 1

ChecksCTM(Drift, Sigma.broken) %>% try()
```

Works.

## 0 in diagonal

```{r}
Sigma.broken <- matrix(c(0, 1, 1, 0), nrow = 2)

ChecksCTM(Drift, Sigma.broken) %>% try()
```

Works.

## Not positive definite

See above.



# Gamma

## More rows

```{r}
Gamma.broken <- rbind(Gamma, c(1, 1))

ChecksCTM(Drift, Gamma = Gamma.broken) %>% try()
```

## More columns

```{r}
Gamma.broken <- cbind(Gamma, c(1, 1))

ChecksCTM(Drift, Gamma = Gamma.broken) %>% try()
```

## NAs

```{r}
Gamma.broken <- Gamma
Gamma.broken[1,1] <- NA

ChecksCTM(Drift, Gamma = Gamma.broken) %>% try()
```

Added an error for NAs in Gamma.

## Non-numbers

```{r}
Gamma.broken <- Gamma
Gamma.broken[1,1] <- "text"

ChecksCTM(Drift, Gamma = Gamma.broken) %>% try()
```

## 0 in diagonal

```{r}
Gamma.broken <- matrix(c(0, 1, 1, 0), nrow = 2)

ChecksCTM(Drift, Gamma = Gamma.broken) %>% try()
```

Works; shows problems

## Not positive definite

See above.


