---
title: "CTmeta function documentation"
author: "Judith Neve"
date: "25/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries}
library(CTmeta)
library(restriktor)
```

This document contains the documentation of the CTmeta function and

- corrects the language at times (e.g. to make it more understandable)
- notes things that need to be specified further

All comments are preceded by the initials of the commenter. When the comment is in a code chunk, there are two hashtags before the initials.

JN: throughout the document, change 's plurals to either just s or "word"s

# CTmeta

## Description, Usage, Arguments, Value

```{r}
?CTmeta

# as a whole: first specify the format of the input, then what it corresponds to - Alex and Rebecca, do you agree?
# all will be adapted slightly based on the input tests

# CTmeta(                # Continuous-time meta-analysis (CTmeta) on standardized lagged effects (Phi) taking into account the various time-intervals used in the primary studies. There is also an interactive web application on my website to perform CTmeta: https://www.uu.nl/staff/RMKuiper/Websites%20%2F%20Shiny%20apps. --- clear description
#   N,                   # change the format in which the matrix dimensions are given.
                         # specify N can be a vector of length S
#   DeltaT,              # change the format in which the matrix dimensions are given.
#   DeltaTStar,
#   Phi,                 # "one can use the function 'TransPhi_Corr" to "the function 'TransPhi_Corr' can be used"
#                        # change the format of the dimensions
#   SigmaVAR = NULL,     # change the format of the dimensions (same problem as for Phi)
#   Gamma = NULL,        # change the format of the dimensions (same problem as for Phi and SigmaVAR)
#                        # also: would it be okay to say "contemporary" instead of "contemporaneous"?
#   Moderators = 0,
#   Mod = NULL,          # change the format of the dimensions
#                        # specify what m is
#   FEorRE = 1,          # can we change the name of the parameter?
#                        # would also be much better to not use 1/2 as input
#   BetweenLevel = NULL, # extra comma not needed in "It will only be used,"
#                        # not "==" but "="
#                        # how it works should be clearer
#   Label = NULL,        # should add a comma after "forest plot"
#                        # "a q*" instead of "an q*"
#                        # "It will only be used, in case the multivariate approach can be used (in case of the univariate approach, it will always use the labeling Study 1 to Study S)" should be "It will only be used when the multivariate approach can be used (in case of the univariate approach, it will always use the labeling Study 1 to Study S)"
#   alpha = 0.05,        # punctuation ";" could be ","
#   PrintPlot = FALSE
# )

# Value

# The output comprises, among others, the overall vectorized transformed standardized lagged effects, their covariance matrix, and the corresponding elliptical/multivariate 95% CI.

# this is clear
```

## Examples

```{r example setup}
##################################################################################################
# Input needed in examples below with q=2 variables and S=3 primary studies
#
N <- matrix(c(643, 651, 473))
DeltaT <- matrix(c(2, 3, 1))
DeltaTStar <- 1
#
# I will use the example matrices stored in the package:
## JN: "we will use"?
Phi <- myPhi
SigmaVAR <- mySigmaVAR
Gamma <- myGamma # Note: CTmeta does not need both SigmaVAR and Gamma, as denomstrated below.
# These are all three stacked matrices of size S*q times q.
## JN: clarify dimensions in previous line
# The CTmeta function will standardize these matrices (to make comparison of effects meaningful).
#
Moderators = 0 # By default set to 0. Hence, not per se needed, as demonstrated below.
## JN: in previous line, should be <- instead of = for consistency
##################################################################################################
```

Note on format: a line just goes until the end of the line and needs side-wise scrolling in the help box. Can this be changed?

```{r examples intro}
# Below, you can find example code. Note that, here, only 3 primary studies are used.
# In practice, one would normally have (many) more, but the code stays (more or less) the same.
## JN: In practice, there would normally be (many) more
```

### Without comments

#### Without moderators

```{r fixed effects model}
### Examples without comments ###
## JN: do we need this separation? (discussion in Teams)

## Example without moderators ##

# Fixed effects model #

# Run CTmeta
CTma <- CTmeta(N,
               DeltaT,
               DeltaTStar,
               Phi,
               SigmaVAR)
CTma
## JN: I would change "messageMultivar" to not have "Hence,"
summary(CTma)
```

```{r Random effects (RE) model}
# Random effects (RE) model #

CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, # JN: as above
       FEorRE = 2)                           # JN: changing the default "FE" to "RE"
## JN: why is this example not getting saved and summary'd?

BetweenLevel <- c(1, 1, 2) # Assuming the first two studies used the same sample/dataset
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, FEorRE = 2,
       BetweenLevel = BetweenLevel) # Two-level RE meta-analysis example
## JN: why is it not saved and summarised?
```

#### With moderators

```{r Moderators fixed effects}
## Example with moderators ##

Mod <- matrix(c(64,65,47)) # 1 moderator
CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR,
               Moderators = 1,
               Mod = Mod) # fixed effects model
summary(CTma)
```

```{r 2 moderators random effects}
q <- dim(Phi)[2]; Mod <- matrix(cbind(c(64,65,47), c(78,89,34)), ncol = q); colnames(Mod) <- c("Mod1", "Mod2") # two moderators, in each column 1
## JN: comment in previous line should be changed to "one in each column"
## JN: why is this all on the same line?
## JN: there should be a comment to explain why q is dim(Phi)[2]

CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Moderators = 1, Mod = Mod,
               FEorRE = 2); CTma$tau2 # random effects model
## JN: why two commands on the same line?
summary(CTma)
```

```{r 1 moderator 2-level RE}
Mod <- matrix(c(64,65,47)) # 1 moderator
BetweenLevel <- c(1, 1, 2) # Assuming the first two studies used the same sample/dataset.
## JN: the way BetweenLevel works should be clarified
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Moderators = 1, Mod = Mod, FEorRE = 2, BetweenLevel = BetweenLevel) # Two-level RE meta-analysis example
## JN: why is this not saved and summarised?
```

```{r funnel/forest plots}
## funnel and forest plots ##
CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, FEorRE = 2)
funnel(CTma$summaryMetaAnalysis, label = 'out')
forest(CTma$summaryMetaAnalysis)
# One can do the same for the two-level analysis.
## JN: "The same can be done for the two-level analysis"
#
# Note, in case a univariate approach had to be taken, leading to multiple analyses, then one should create a plot per analysis:
## JN: Note that when a univariate approach is taken (leading to multiple analysis), there should be one plot per analysis:
# lapply(CTma$summaryMetaAnalysis_jk, funnel, label = 'out')
#
# In case you want to create a plot per element of the study-specific Phi's:
## JN: "To create a plot per element of the ... Phis"
#elt <- rep(F, (q*q))
#elt[1] <- T # First element out of q*q true, so referring to element Phi11.
#yi_Phi11 <- CTma$summaryMetaAnalysis$yi[elt]
#vi_Phi11 <- CTma$summaryMetaAnalysis$vi[elt]
#funnel(yi_Phi11, vi_Phi11, label = 'out')
#forest(yi_Phi11, vi_Phi11)
elt <- rep(F, (q*q))
## JN: why is it called "elt"? What does that stand for?
elt[2] <- T # Second element out of q*q true, so referring to element Phi12.
yi_Phi12 <- CTma$summaryMetaAnalysis$yi[elt]
vi_Phi12 <- CTma$summaryMetaAnalysis$vi[elt]
funnel(yi_Phi12, vi_Phi12, label = 'out')
forest(yi_Phi12, vi_Phi12)
```

```{r phiplot}
## Make customized Phi-plot of resulting overall Phi ##
## JN: specify this is simply creating the same plot by hand
## JN: "Making"

CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, PrintPlot = TRUE)
CTma$PhiPlot

out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
overallPhi <- out_CTmeta$Overall_standPhi
Title <- as.list(expression(paste0(Phi(Delta[t]), " plot:"),
   "How do the overall lagged parameters vary as a function of the time-interval"))
## JN: change title, it shows wrong
PhiPlot(DeltaTStar, overallPhi, Min = 0, Max = 40, Step = 0.5, Title = Title)
# or
ggPhiPlot <- ggPhiPlot(DeltaTStar, overallPhi, Min = 0, Max = 40, Step = 0.5, Title = Title)
ggPhiPlot$PhiPlot
```

```{r goric}
## Evaluate dominance of (absolute values of) cross-lagged effects ##
## JN: "Evaluating the dominance ..."

if (!require("restriktor")) install.packages("restriktor") # Use restriktor package for function goric().
## JN: "the function goric is in the restriktor package"
                                                           # Authors of goric(): Vanbrabant and Kuiper.
library(restriktor)

out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
H1 <- "abs(overallPhi12) < abs(overallPhi21)"
goric(out_CTmeta, H1, type = "gorica", comparison = "complement")
## JN: won't work if another package with a function called "goric" is loaded, regardless of the order they were loaded in

out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
H1 <- "abs(overallPhi12) < abs(overallPhi21); abs(overallPhi11) < abs(overallPhi22)"
goric(out_CTmeta, H1, type = "gorica", comparison = "complement")

out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
est <- coef(out_CTmeta)  # or: est  <- out_CTmeta$Overall_vecStandPhi_DeltaTStar
VCOV <- vcov(out_CTmeta) # or: VCOV <- out_CTmeta$CovMx_OverallPhi_DeltaTStar
goric(est, VCOV = VCOV, H1, type = "gorica", comparison = "complement")
```

```{r lagged correlation matrix}
## What if primary studies report a (lagged) correlation matrix ##
## JN: add a question mark

q <- 2
corr_YXYX <- matrix(c(1.00, 0.40, 0.63, 0.34,
                      0.40, 1.00, 0.31, 0.63,
                      0.63, 0.31, 1.00, 0.41,
                      0.34, 0.63, 0.41, 1.00), byrow = T, ncol = 2*q)
N <- matrix(c(643, 651, 473))
DeltaT <- matrix(c(2, 3, 1))
DeltaTStar <- 1
#
# Create input:
out_1 <- TransPhi_Corr(DeltaTStar = DeltaT[1], DeltaT = 1, N = N[1], corr_YXYX)
Phi_1 <- out_1$standPhi_DeltaTStar
SigmaVAR_1 <- out_1$standSigmaVAR_DeltaTStar
out_2 <- TransPhi_Corr(DeltaTStar = DeltaT[2], DeltaT = 1, N = N[2], corr_YXYX)
Phi_2 <- out_2$standPhi_DeltaTStar
SigmaVAR_2 <- out_2$standSigmaVAR_DeltaTStar
out_3 <- TransPhi_Corr(DeltaTStar = DeltaT[3], DeltaT = 1, N = N[3], corr_YXYX)
Phi_3 <- out_3$standPhi_DeltaTStar
SigmaVAR_3 <- out_3$standSigmaVAR_DeltaTStar
#
Phi <- rbind(Phi_1, Phi_2, Phi_3) # This, returns a stacked matrix of size S q times q.
## JN: this comment should not have a comma
SigmaVAR <- rbind(SigmaVAR_1, SigmaVAR_2, SigmaVAR_3)
out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
## JN: why is there no summary of this?
out_CTmeta$Overall_standPhi
```

##############################

### Examples with comments

JN: this section lengthens the documentation considerably and has little more information than the previous section. I believe it would be best to combine them.

```{r}
### Examples with comments ###


## Example without moderators ##

# Fixed effects model #

# Run CTmeta with, for instance,
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)

# There are multiple options; use one of the following:
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Gamma, Moderators, Mod, 1) # The 1, here, says FEorRE = 1
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Gamma, Moderators, Mod)    # Notably, if Moderators = 0, 'Mod' is not inspected.
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Gamma, Moderators)
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Gamma)
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)        # Says, implicitly, Gamma = NULL
CTmeta(N, DeltaT, DeltaTStar, Phi, Gamma = Gamma)   # Says, implicitly, SigmaVAR = NULL
CTmeta(N, DeltaT, DeltaTStar, Phi, NULL, Gamma)     # Says SigmaVAR = NULL
## JN: whange comments - remove commas, clarify language

# Note: Do NOT use
#CTmeta(N, DeltaT, DeltaTStar, Phi, Gamma)
## JN: add a space between # and CTmeta
# Then, CTmeta incorrectly uses SigmaVAR = Gamma.
## JN: rephrase this
```

```{r commented output}
# Different types of output options are possible:
CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
CTma # gives same as print(CTma)
## JN: "this is equivalent to"
summary(CTma)
print(CTma, digits = 4)
## JN: this only changes when run in the console. Specify this in a comment
summary(CTma, digits = 4)
# In Rstudio, use 'CTma$' to see what output there is. For example:
## JN: "In Rstudio, using "CTMA$" lets you see what the output consists of. For example:"
CTma$summaryMetaAnalysis
```

```{r}
# Random effects model #

# Add "FEorRE = 2"; e.g.,
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, FEorRE = 2)

# Two-level RE meta-analysis example
BetweenLevel <- c(1, 1, 2) # Assuming the first two studies used the same sample/dataset
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, FEorRE = 2, BetweenLevel = BetweenLevel) # Two-level RE meta-analysis example
# Note, one can also use this in case there are moderators (as in the example below).
## JN: only the previous comment was added.
```

```{r}
## Example with moderators ##

Mod <- matrix(c(64,65,47)) # 1 moderator
#q <- dim(Phi)[2]; Mod <- matrix(cbind(c(64,65,47), c(78,89,34)), ncol = q); colnames(Mod) <- c("Mod1", "Mod2") # two moderators, in each column 1
## JN: why is this commented out? i.e. why are we not fitting a model with two moderators?
CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Moderators = 1, Mod = Mod) # fixed effects model
#CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Moderators = 1, Mod = Mod, FEorRE = 2); CTma$tau2 # random effects model
summary(CTma)
## JN: why is some of the code commented out?
```

```{r}
# Two-level RE meta-analysis example
Mod <- matrix(c(64,65,47)) # 1 moderator
BetweenLevel <- c(1, 1, 2) # Assuming the first two studies used the same sample/dataset
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Moderators = 1, Mod = Mod, FEorRE = 2, BetweenLevel = BetweenLevel) # Two-level RE meta-analysis example
## JN: this has no extra information
```

```{r}
## funnel and forest plots ##
CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, FEorRE = 2)
funnel(CTma$summaryMetaAnalysis, label = 'out')
forest(CTma$summaryMetaAnalysis)
# One can do the same for the two-level analysis.
#
# Note, in case a univariate approach had to be taken, leading to multiple analyses, then one should create a plot per analysis:
# lapply(CTma$summaryMetaAnalysis_jk, funnel, label = 'out')
#
## JN: there is no extra information here
```

```{r}
# Notes on funnel and forest:
# - These plots are now based on the q*q elements in the study-specific Phi's and the S studies.
# See below, how you can create these plots per element of Phi. This should then be done separately for all q*q elements.
# - In case label names are too long or not insightful, one can change them by using the Label argument.
# In case of the funnel plot, one can also decide to not use the "label = 'out'" part.

#
# Notes on forest:
# - For random-effects models of class "rma.mv" (see rma.mv) with multiple  values, the addpred argument can be used to specify for which level of the inner factor the prediction interval should be provided (since the intervals differ depending on the value).
# - One can also look into the functionality of addpoly().

## JN: these notes are extra compared to the previous part. They should also be rephrased
```

```{r}
#
# In case you want to create a plot per element of the study-specific Phi's:
#elt <- rep(F, (q*q))
#elt[1] <- T # First element out of q*q true, so referring to element Phi11.
#yi_Phi11 <- CTma$summaryMetaAnalysis$yi[elt]
#vi_Phi11 <- CTma$summaryMetaAnalysis$vi[elt]
#funnel(yi_Phi11, vi_Phi11, label = 'out')
#forest(yi_Phi11, vi_Phi11)
elt <- rep(F, (q*q))
elt[2] <- T # Second element out of q*q true, so referring to element Phi12.
yi_Phi12 <- CTma$summaryMetaAnalysis$yi[elt]
vi_Phi12 <- CTma$summaryMetaAnalysis$vi[elt]
funnel(yi_Phi12, vi_Phi12, label = 'out')
forest(yi_Phi12, vi_Phi12)
## JN: this is identical to the previous part
```

```{r comments making Phi Plot}
## Make customized Phi-plot of resulting overall Phi ##

# Option 1: Using the plot option in the function:
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, PrintPlot = TRUE)
# The plot can be stored and retrieved as an object as follows:
## JN: "We can store the plot as an object as follows:"
# CTma <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, PrintPlot = TRUE)
## JN: add "If the plot is tored as an object, we can retrive it as follows:"
# CTma$PhiPlot

## JN: this is clearer, why the version with no comments? would also uncomment the two code lines


# Option 2: A customized Phi-plot can be made using the function 'PhiPlot' (see below) or by using the interactive web app from my website (\url{https://www.uu.nl/staff/RMKuiper/Websites\%20\%2F\%20Shiny\%20apps}).
## JN: the url formatting shows in the documentation
# Alternatively, one can use the function 'ggPhiPlot' instead of 'PhiPlot'.
## JN: "Alternatively, "ggPhiPlot" can be used instead of "PhiPlot"."

# Extract the (q times q) overall Phi matrix
## JN: change the line spacing
## JN: rephrase (q times q)
out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
# resulting overall Phi:
overallPhi <- out_CTmeta$Overall_standPhi
## JN: better explained

# Make Phi-plot:
Title <- as.list(expression(paste0(Phi(Delta[t]), " plot:"),
   "How do the overall lagged parameters vary as a function of the time-interval"))
PhiPlot(DeltaTStar, overallPhi, Min = 0, Max = 40, Step = 0.5, Title = Title)
# or
ggPhiPlot(DeltaTStar, overallPhi, Min = 0, Max = 40, Step = 0.5, Title = Title)
# The plot can be stored and retrieved as an object as follows:
# ggPhiPlot <- ggPhiPlot(DeltaTStar, overallPhi, Min = 0, Max = 40, Step = 0.5, Title = Title)
# ggPhiPlot$PhiPlot

## JN: I would uncomment the last two lines
```

```{r commented goric}
## Evaluate dominance of (absolute values of) cross-lagged effects ##

if (!require("restriktor")) install.packages("restriktor") # Use restriktor package for function goric().
                                                           # Authors of goric(): Vanbrabant and Kuiper.
#
# If version from github needed:
#if (!require("devtools")) install.packages("devtools")
#library(devtools)
#install_github("LeonardV/restriktor")

## JN: information above has been added. Slightly change the language

#
library(restriktor)

# Option 1
# Use CTmeta object
## JN: "Using a CTmeta object"
out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
#
# Example 1: dominance of (absolute values of) cross-lagged effects
# Specify hypothesis
## JN: "Specifying the hypothesis"
H1 <- "abs(overallPhi12) < abs(overallPhi21)"
#H2 <- "abs(overallPhi12) > abs(overallPhi21)" # = complement of H1 and does not need to be specified, see below.
## JN: put the comment on a separate line
# Evaluate dominance of cross-lagged effects via AIC-type criterion called the GORICA (Altinisik, Nederhof, Hoijtink, Oldehinkel, Kuiper, accepted 2021).
## JN: "Evaluating the..."
#goric(out_CTmeta, H1, H2, type = "gorica", comparison = "none")
# or, since H2 is complement of H1, equivalently:
goric(out_CTmeta, H1, type = "gorica", comparison = "complement")

#
# Example 2: dominance of (absolute values of) cross-lagged effects and autoregressive effects
H1 <- "abs(overallPhi12) < abs(overallPhi21); abs(overallPhi11) < abs(overallPhi22)"
# Note that, now, specification of complement 'by hand' harder.
goric(out_CTmeta, H1, type = "gorica", comparison = "complement")
#

#
# Option 2
# Extract the vectorized overall standardized overallPhi matrix and its covariance matrix
# using the functions coef() and vcov()
out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
est <- coef(out_CTmeta)  # or: est  <- out_CTmeta$Overall_vecStandPhi_DeltaTStar
VCOV <- vcov(out_CTmeta) # or: VCOV <- out_CTmeta$CovMx_OverallPhi_DeltaTStar
goric(est, VCOV = VCOV, H1, type = "gorica", comparison = "complement")

## What if primary studies report a (lagged) correlation matrix ##

# Suppose, for ease, that all S=3 primary studies reported the following lagged correlation matrix:
q <- 2
corr_YXYX <- matrix(c(1.00, 0.40, 0.63, 0.34,
                      0.40, 1.00, 0.31, 0.63,
                      0.63, 0.31, 1.00, 0.41,
                      0.34, 0.63, 0.41, 1.00), byrow = T, ncol = 2*q)

# In the example below, the same N and DeltaT(Star) values are used:
N <- matrix(c(643, 651, 473))
DeltaT <- matrix(c(2, 3, 1))
DeltaTStar <- 1

# Use the function 'TransPhi_Corr' to calculate the corresponding standardized lagged effects matrix per primary study.
# Note that one can already make the time-intervals equal via the arguments DeltaTStar and DeltaT, but CTmeta can as well.
# In this example, I deliberately make the time-intervals unequal, such that the example is in line with the input (i.e., DeltaT <- matrix(c(2, 3, 1))) and such the resulting overall Phi should equal the Phi that underlies this lagged correlation matrix (which I check at the end).

## JN: more info here. change the language a little bit

out_1 <- TransPhi_Corr(DeltaTStar = DeltaT[1], DeltaT = 1, N = N[1], corr_YXYX)
Phi_1 <- out_1$standPhi_DeltaTStar
SigmaVAR_1 <- out_1$standSigmaVAR_DeltaTStar
out_2 <- TransPhi_Corr(DeltaTStar = DeltaT[2], DeltaT = 1, N = N[2], corr_YXYX)
Phi_2 <- out_2$standPhi_DeltaTStar
SigmaVAR_2 <- out_2$standSigmaVAR_DeltaTStar
out_3 <- TransPhi_Corr(DeltaTStar = DeltaT[3], DeltaT = 1, N = N[3], corr_YXYX)
Phi_3 <- out_3$standPhi_DeltaTStar
SigmaVAR_3 <- out_3$standSigmaVAR_DeltaTStar

# Make Phi
## JN: this comment was added and makes this easier to understand. Change the language
Phi <- rbind(Phi_1, Phi_2, Phi_3) # This, returns a stacked matrix of size S q times q.
## JN: change the language of the comment
SigmaVAR <- rbind(SigmaVAR_1, SigmaVAR_2, SigmaVAR_3)
# For more details, see ?TransPhi_Corr

# The example CTmeta() code above can be run using this Phi; e.g.,
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
## JN: why is this here since it's ran and saved just below?

# The overall q-times-q (here, 2x2) lagged effects matrix Phi
out_CTmeta <- CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR)
out_CTmeta$Overall_standPhi
#
# As a check, to see indeed that CTmeta works properly (where the resulting Phi is independent of the choise of N).
## JN: change this comment
TransPhi_Corr(DeltaTStar = 1, DeltaT = 1, N = 100, corr_YXYX)$standPhi_DeltaTStar
# Note that is normally not a check you would do.
## JN: change this comment
```

