---
title: "CTmeta function documentation"
author: "Judith Neve"
date: "25/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries}
library(CTmeta)
library(restriktor)
```

This document contains the documentation of the CTmeta function and

- corrects the language at times (e.g. to make it more understandable)
- notes things that need to be specified further

All comments are preceded by the initials of the commenter. When the comment is in a code chunk, there are two hashtags before the initials.

JN: throughout the document, change 's plurals to either just s or "word"s

# CTmeta

## Description, Usage, Arguments, Value

```{r}
?CTmeta

## as a whole: first specify the format of the input, then what it corresponds to - Alex and Rebecca, do you agree?

# CTmeta(
#   N,                   ## is it -1 only for time series or both?
#   DeltaT,
#   DeltaTStar,
#   Phi,                 ## include an example where Phi is an array
#   SigmaVAR = NULL,     ## include an example where SigmaVAR is an array
#   Gamma = NULL,        ## would it be okay to say "contemporary" instead of "contemporaneous"?
#   Moderators = 0,
#   Mod = NULL,
#   FEorRE = 1,
#   BetweenLevel = NULL, ## how it works should be clearer
                         ## it can be a factor in practice - is it meant to be this way??
#   Label = NULL,        ## still need to figure out how this works
#   alpha = 0.05,
#   PrintPlot = FALSE    ### only works when no moderators
# )

# Value

# The output comprises, among others, the overall vectorized transformed standardized lagged effects, their covariance matrix, and the corresponding elliptical/multivariate 95% CI.
```

## Examples

```{r example setup}
##################################################################################################
# Input needed in examples below with q=2 variables and S=3 primary studies
#
N <- matrix(c(643, 651, 473))
DeltaT <- matrix(c(2, 3, 1))
DeltaTStar <- 1
#
# I will use the example matrices stored in the package:
Phi <- myPhi
SigmaVAR <- mySigmaVAR
Gamma <- myGamma # Note: CTmeta does not need both SigmaVAR and Gamma, as denomstrated below.
# These are all three stacked matrices of size S*q times q.
# The CTmeta function will standardize these matrices (to make comparison of effects meaningful).
#
Moderators = 0 # By default set to 0. Hence, not per se needed, as demonstrated below.
##################################################################################################
```

Note on format: a line just goes until the end of the line and needs side-wise scrolling in the help box. Can this be changed?

```{r 1 moderator 2-level RE}
Mod <- matrix(c(64,65,47)) # 1 moderator
BetweenLevel <- c(1, 1, 2) # Assuming the first two studies used the same sample/dataset.
## JN: the way BetweenLevel works should be clarified
CTmeta(N, DeltaT, DeltaTStar, Phi, SigmaVAR, Moderators = 1, Mod = Mod, FEorRE = 2, BetweenLevel = BetweenLevel) # Two-level RE meta-analysis example
```

