---
title: "Testing the input and output of Area"
author: "Judith Neve"
date: "20/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(CTmeta)
```

This document tests what can be used as input and output for the function Area. Each argument is examined in turn, and at the end some additional checks are done to verify plots can be made for different configurations of the model.

Where the function runs, the output is compared to the expected output.

After every attempt to "break" the function, a diagnostic is written as a comment in the code chunk, and the code chunk is followed by a "to do" list to indicate what needs to be specified/improved/changed in the function documentation or the function itself.

Original example:

```{r}
DeltaT <- 1
Phi <- myPhi[1:2, 1:2]
#
q <- dim(Phi)[1]
SigmaVAR <- diag(q) # for ease
#
Gamma <- Gamma.fromVAR(Phi, SigmaVAR)
##################################################################################################

CTMpar <- CTMparam(DeltaT, Phi, SigmaVAR)
```


# DeltaT

## DeltaT = 2

```{r}
CTMpar.break <- CTMparam(DeltaT = 2, Phi, SigmaVAR)

summary(CTMpar.break) == summary(CTMpar)
CTMpar.break$standSigma == CTMpar$standSigma
```

Looks like it works!


## DeltaT = Inf

```{r}
CTMpar.break <- CTMparam(DeltaT = Inf, Phi, SigmaVAR)
CTMpar.break
summary(CTMpar.break) == summary(CTMpar)
CTMpar.break$standSigma == CTMpar$standSigma
```

This is ok - the results are enough to show there may be something wrong + specifies the process in not stable

## DeltaT = 0

```{r}
CTMpar.break <- CTMparam(DeltaT = 0, Phi, SigmaVAR) %>% try()
```

## DeltaT = -1

```{r}
CTMpar.break <- CTMparam(DeltaT = -1, Phi, SigmaVAR)
CTMpar.break
summary(CTMpar.break) == summary(CTMpar)
CTMpar.break$standSigma == CTMpar$standSigma
```

Negative values will work, but there is a message in the output that shows this is not ideal. We can keep this.

## DeltaT = c(1, 0)

```{r}
CTMpar.break <- CTMparam(DeltaT = c(1, 0), Phi, SigmaVAR) %>% try()
```

## DeltaT = TRUE

```{r}
CTMpar.break <- CTMparam(DeltaT = TRUE, Phi, SigmaVAR)
CTMpar.break
summary(CTMpar.break) == summary(CTMpar)
CTMpar.break$standSigma == CTMpar$standSigma
```

TRUE is converted to 1. That's ok.

## DeltaT = "text"

```{r}
CTMpar.break <- CTMparam(DeltaT = "text", Phi, SigmaVAR) %>% try()
```

The error does suggest DeltaT or Phi is the problem. No need for further checks.

## DeltaT = NA

```{r}
CTMpar.break <- CTMparam(DeltaT = NA, Phi, SigmaVAR) %>% try()
```

This runs well.


# SigmaVAR

## SigmaVAR with NAs

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break[2,1] <- NA

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR.break) %>% try()
```

## SigmaVAR with text

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break[2,1] <- "text"

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR.break) %>% try()
```

## SigmaVAR with 1 extra row

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break <- rbind(SigmaVAR.break, c(1,1))

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR.break) %>% try()
```

## SigmaVAR with 1 extra col

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break <- cbind(SigmaVAR.break, c(1,1))

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR.break) %>% try()
```

## SigmaVAR with 1 extra row and 1 extra col

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break <- cbind(SigmaVAR.break, c(1,1))
SigmaVAR.break <- rbind(SigmaVAR.break, c(1,1,1))

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR.break) %>% try()
```

## SigmaVAR a vector

```{r}
SigmaVAR.break <- SigmaVAR %>% as.vector()

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR.break) %>% try()
```

## Both SigmaVAR and Gamma - which one gets used?

```{r}
CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR, Gamma = Gamma)
CTMpar.break
```

We first input a mismatched Gamma.

```{r}
Gamma.break <- Gamma
Gamma.break[1,1] <- 10

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR, Gamma = Gamma.break)
CTMpar.break

summary(CTMpar.break) == summary(CTMpar)
CTMpar.break$standSigma == CTMpar$standSigma
```

Gamma is used.

We input a mismatched SigmaVAR.

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break[1,1] <- 10

CTMpar.break <- CTMparam(DeltaT, Phi, SigmaVAR = SigmaVAR.break, Gamma = Gamma)
CTMpar.break

summary(CTMpar.break) == summary(CTMpar)
CTMpar.break$standSigma == CTMpar$standSigma
```

SigmaVAR is also used.

Added a warning that says they are mismatched.



# Gamma

## Gamma with NAs

```{r}
Gamma.break <- Gamma
Gamma.break[2,1] <- NA

CTMpar.break <- CTMparam(DeltaT, Phi, Gamma = Gamma.break)
CTMpar.break
```

NA values appear but some things are still in. This should be fine.

## Gamma with text

```{r}
Gamma.break <- Gamma
Gamma.break[2,1] <- "text"

CTMpar.break <- CTMparam(DeltaT, Phi, Gamma = Gamma.break) %>% try()
```

## Gamma with 1 extra row

```{r}
Gamma.break <- Gamma
Gamma.break <- rbind(Gamma.break, c(1,1))

CTMpar.break <- CTMparam(DeltaT, Phi, Gamma = Gamma.break) %>% try()
```

Proper break.

## Gamma with 1 extra col

```{r}
Gamma.break <- Gamma
Gamma.break <- cbind(Gamma.break, c(1,1))

CTMpar.break <- CTMparam(DeltaT, Phi, Gamma = Gamma.break) %>% try()
```

Proper break.

## Gamma with 1 extra row and 1 extra col

```{r}
Gamma.break <- Gamma
Gamma.break <- cbind(Gamma.break, c(1,1))
Gamma.break <- rbind(Gamma.break, c(1,1,1))

CTMpar.break <- CTMparam(DeltaT, Phi, Gamma = Gamma.break) %>% try()
```

Proper break.

## Gamma a vector

```{r}
Gamma.break <- Gamma %>% as.vector()

CTMpar.break <- CTMparam(DeltaT, Phi, Gamma = Gamma.break) %>% try()
```

Proper break.



# Phi

## Phi with NAs

```{r}
Phi.break <- Phi
Phi.break[2,1] <- NA

CTMpar.break <- CTMparam(DeltaT, Phi.break, SigmaVAR) %>% try()
```

The error message.

## Phi with text

```{r}
Phi.break <- Phi
Phi.break[2,1] <- "text"

CTMpar.break <- CTMparam(DeltaT, Phi.break, SigmaVAR) %>% try()
```

Error message added.

## Phi with 1 extra row

```{r}
Phi.break <- Phi
Phi.break <- rbind(Phi.break, c(1,1))

CTMpar.break <- CTMparam(DeltaT, Phi.break, SigmaVAR) %>% try()
```

Error message added.

## Phi with 1 extra col

```{r}
Phi.break <- Phi
Phi.break <- cbind(Phi.break, c(1,1))

CTMpar.break <- CTMparam(DeltaT, Phi.break, SigmaVAR) %>% try()
```

Error message added.

## Phi with 1 extra row and 1 extra col but normal size SigmaVAR

```{r}
Phi.break <- Phi
Phi.break <- rbind(Phi.break, c(1,1))
Phi.break <- cbind(Phi.break, c(1,1,1))

CTMpar.break <- CTMparam(DeltaT, Phi.break, SigmaVAR) %>% try()
```

Error message is about SigmaVAR, not Phi.

## Phi with 1 extra row and 1 extra col but larger SigmaVAR

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break <- rbind(SigmaVAR.break, c(1,1))
SigmaVAR.break <- cbind(SigmaVAR.break, c(1,1,1))

CTMpar.break <- CTMparam(DeltaT, Phi.break, SigmaVAR.break) %>% try()
```

This would likely run fine if the matrices were from actual data - there is no warning about size.

## Phi a vector

```{r}
Phi.break <- Phi %>% as.vector()

CTMpar.break <- CTMparam(DeltaT, Phi.break, SigmaVAR) %>% try()
```
