---
title: "Testing the input and output of Area"
author: "Judith Neve"
date: "20/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(CTmeta)
```

This document tests what can be used as input and output for the function Area. Each argument is examined in turn, and at the end some additional checks are done to verify plots can be made for different configurations of the model.

Where the function runs, the output is compared to the expected output.

After every attempt to "break" the function, a diagnostic is written as a comment in the code chunk, and the code chunk is followed by a "to do" list to indicate what needs to be specified/improved/changed in the function documentation or the function itself.

Original example:

```{r}
Phi <- myPhi[1:2, 1:2] # = Phi(1), that is, Phi when DeltaT = 1
q <- dim(Phi)[1]
#SigmaVAR <- diag(q) # Then, DeltaT_diag = 1 (since, implicitly, DeltaT = 1)
Gamma <- matrix(c(1, 0.5, 0.4, 1), byrow = T, nrow = q, ncol = q)
SigmaVAR <- Gamma - Phi %*% Gamma %*% t(Phi)
##################################################################################################

DiagDeltaT.obj <- DiagDeltaT(Phi, SigmaVAR)
```

# Phi

## Phi with NA

## Non-numeric Phi

## Phi with one more row

## Phi with one more col

## Phi with one more row and one more col

## Phi and Drift (broken)

Probably add a message/warning here

## Phi (broken) and Drift


# SigmaVAR

## SigmaVAR with NA

## Non-numeric SigmaVAR

## SigmaVAR with one more row

## SigmaVAR with one more col

## SigmaVAR with one more row and one more col

## SigmaVAR and Sigma (broken)

Probably add a message/warning here

## SigmmaVAR and Gamma (broken)

Probably add a message/warning here

## SigmaVAR (broken) and Sigma

## SigmaVAR (broken) and Gamma


# Drift

## Drift with NA

## Non-numeric Drift

## Drift with one more row

## Drift with one more col

## Drift with one more row and one more col


# Sigma

## Sigma with NA

## Non-numeric Sigma

## Sigma with one more row

## Sigma with one more col

## Sigma with one more row and one more col

## Sigma and Gamma (broken)

## Sigma (broken) and Gamma


# Gamma

## Gamma with NA

## Non-numeric Gamma

## Gamma with one more row

## Gamma with one more col

## Gamma with one more row and one more col


# xstart_DeltaT

## xstart_deltaT = 0

## xstart_DeltaT = 1.5

## xstart_DeltaT = "text"

## xstart_DeltaT = NA

## xstart_DeltaT = NULL

## xstart_DeltaT = c(1, 2, 3)

## xstart_DeltaT = c(4, 2, 3)
