---
title: "Testing the input and output of Area"
author: "Judith Neve"
date: "20/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(CTmeta)
```

This document tests what can be used as input and output for the function Area. Each argument is examined in turn, and at the end some additional checks are done to verify plots can be made for different configurations of the model.

Where the function runs, the output is compared to the expected output.

After every attempt to "break" the function, a diagnostic is written as a comment in the code chunk, and the code chunk is followed by a "to do" list to indicate what needs to be specified/improved/changed in the function documentation or the function itself.

Original example:

```{r}
Phi <- myPhi[1:2, 1:2] # = Phi(1), that is, Phi when DeltaT = 1
q <- dim(Phi)[1]
#SigmaVAR <- diag(q) # Then, DeltaT_diag = 1 (since, implicitly, DeltaT = 1)
Gamma <- matrix(c(1, 0.5, 0.4, 1), byrow = T, nrow = q, ncol = q)
SigmaVAR <- Gamma - Phi %*% Gamma %*% t(Phi)
##################################################################################################

DiagDeltaT.obj <- DiagDeltaT(Phi, SigmaVAR)
```


# Phi

## Phi with NA

```{r}
Phi.break <- Phi
Phi.break[1,2] <- NA

DiagDeltaT(Phi.break, SigmaVAR) %>% try()
```

Shows there is a problem with Phi. No need for an error message


## Non-numeric Phi

```{r}
Phi.break <- Phi
Phi.break[1,2] <- "text"

DiagDeltaT(Phi.break, SigmaVAR) %>% try()
```

Shows there is a problem with Phi. No need for an error message

## Phi with one more row

```{r}
Phi.break <- rbind(Phi, c(1,1))

DiagDeltaT(Phi.break, SigmaVAR) %>% try()
```

Appropriate error message

## Phi with one more col

```{r}
Phi.break <- cbind(Phi, c(1,1))

DiagDeltaT(Phi.break, SigmaVAR) %>% try()
```

Appropriate error message

## Phi with one more row and one more col

```{r}
Phi.break <- matrix(data = c(16, -8, -4, -8, 29, 12, -4, 12, 41), nrow = 3, ncol = 3, byrow = TRUE)

DiagDeltaT(Phi.break, SigmaVAR) %>% try()
```

Error is about SigmaVAR but the true issue is they are mismatched. Reuse code from CTMparam to fix this.

Fixed!

## Phi and Drift (broken)

```{r}
Drift.break <- myDrift
Drift.break[1,1] <- NA

DiagDeltaT(Phi, SigmaVAR, Drift = Drift.break) %>% try()
```

Breaks because Drift is broken. Add a warning that Drift is ignored.

Done!

## Phi (broken) and Drift

```{r}
Drift <- myDrift

DiagDeltaT(Phi.break, SigmaVAR, Drift = Drift) %>% try()
```

Returns the expected warning and the error relevant to Phi.



# SigmaVAR

## SigmaVAR with NA

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break[1,2] <- NA

DiagDeltaT(Phi, SigmaVAR.break) %>% try()
```

specify an error message for missing values in SigmaVAR

## Non-numeric SigmaVAR

```{r}
SigmaVAR.break <- SigmaVAR
SigmaVAR.break[1,2] <- "text"

DiagDeltaT(Phi, SigmaVAR.break) %>% try()
```

## SigmaVAR with one more row

```{r}
SigmaVAR.break <- rbind(SigmaVAR, c(1,1))

DiagDeltaT(Phi, SigmaVAR.break) %>% try()
```

## SigmaVAR with one more col

```{r}
SigmaVAR.break <- cbind(SigmaVAR, c(1,1))

DiagDeltaT(Phi, SigmaVAR.break) %>% try()
```

## SigmaVAR with one more row and one more col

```{r}
SigmaVAR.break <- rbind(cbind(SigmaVAR, c(0,0)), c(0,0,1))

DiagDeltaT(Phi, SigmaVAR.break) %>% try()
```

## SigmaVAR and Sigma (broken)

```{r}
Sigma <- diag(2)

Sigma.break <- cbind(Sigma, c(1,1))

DiagDeltaT(Phi, SigmaVAR, Sigma = Sigma.break) %>% try()

DiagDeltaT.obj$SigmaVAR_DeltaT_diag == DiagDeltaT(Phi, SigmaVAR, Sigma = Sigma.break)$SigmaVAR_DeltaT_diag
```

Sigma fully gets ignored. Added a warning


## SigmmaVAR and Gamma (broken)

```{r}
Gamma.break <- cbind(Gamma, c(1,1))

DiagDeltaT(Phi, SigmaVAR, Gamma = Gamma.break) %>% try()
```

Originally not ignored. Added a warning

## SigmaVAR (broken) and Sigma

```{r}
DiagDeltaT(Phi, SigmaVAR.break, Sigma = Sigma) %>% try()
```

## SigmaVAR (broken) and Gamma

```{r}
DiagDeltaT(Phi, SigmaVAR.break, Gamma = Gamma) %>% try()
```


# Drift

## Drift with NA

```{r}
Drift.break <- Drift
Drift.break[1,2] <- NA

DiagDeltaT(Drift = Drift.break, SigmaVAR = SigmaVAR) %>% try()
```

Add an error

## Non-numeric Drift

```{r}
Drift.break <- Drift
Drift.break[1,2] <- "text"

DiagDeltaT(Drift = Drift.break, SigmaVAR = SigmaVAR) %>% try()
```

## Drift with one more row

```{r}
Drift.break <- rbind(Drift, c(0,1))

DiagDeltaT(Drift = Drift.break, SigmaVAR = SigmaVAR) %>% try()
```

From the error message we know to look at Drift

## Drift with one more col

```{r}
Drift.break <- cbind(Drift, c(0,1))

DiagDeltaT(Drift = Drift.break, SigmaVAR = SigmaVAR) %>% try()
```

From the error message we know to look at Drift

## Drift with one more row and one more col

```{r}
Drift.break <- matrix(data = c(16, -8, -4, -8, 29, 12, -4, 12, 41), nrow = 3, ncol = 3, byrow = TRUE)

DiagDeltaT(Drift = Drift.break, SigmaVAR = SigmaVAR) %>% try()
```

Also: cleanup needed for the messages

Done :)


# Sigma

## Sigma with NA

```{r}
Sigma.break <- Sigma
Sigma.break[1,2] <- NA

DiagDeltaT(Phi, Sigma = Sigma.break) %>% try()
```

Clear default error message

## Non-numeric Sigma

```{r}
Sigma.break <- Sigma
Sigma.break[1,2] <- "text"

DiagDeltaT(Phi, Sigma = Sigma.break) %>% try()
```

Clear enough error.

## Sigma with one more row

```{r}
Sigma.break <- rbind(Sigma, c(1,1))

DiagDeltaT(Phi, Sigma = Sigma.break) %>% try()
```

## Sigma with one more col

```{r}
Sigma.break <- cbind(Sigma, c(1,1))

DiagDeltaT(Phi, Sigma = Sigma.break) %>% try()
```

## Sigma with one more row and one more col

```{r}
Sigma.break <- cbind(rbind(Sigma, c(1,1)), c(1,1,1))

DiagDeltaT(Phi, Sigma = Sigma.break) %>% try()
```

## Sigma and Gamma (both working)

```{r}
Sig.Gam <- DiagDeltaT(Phi, Sigma = Sigma, Gamma = Gamma) %>% try()
```

## Sigma and Gamma (broken)

```{r}
Gamma.break <- rbind(Gamma, c(1,1))

DiagDeltaT(Phi, Sigma = Sigma, Gamma = Gamma.break) %>% try()
```

```{r}
Gamma.break <- Gamma
Gamma.break[1,1] <- NA

DiagDeltaT(Phi, Sigma = Sigma, Gamma = Gamma.break) %>% try()
```

The problem is with Gamma, but the error relates to Sigma.

## Sigma (broken) and Gamma

```{r}
Sigma.break <- rbind(Sigma, c(1,1))

DiagDeltaT(Phi, Sigma = Sigma.break, Gamma = Gamma)
Sig.Gam
```

Gamma is used by default. Modify documentation and add a warning.

Done :)


# Gamma

## Gamma with NA

```{r}
Gamma.break <- Gamma
Gamma.break[1,2] <- NA

DiagDeltaT(Phi, Gamma = Gamma.break) %>% try()
```

Add an error.

## Non-numeric Gamma

```{r}
Gamma.break <- Gamma
Gamma.break[1,2] <- "text"

DiagDeltaT(Phi, Gamma = Gamma.break) %>% try()
```

Error works.

## Gamma with one more row

```{r}
Gamma.break <- rbind(Gamma, c(1,1))

DiagDeltaT(Phi, Gamma = Gamma.break) %>% try()
```

## Gamma with one more col

```{r}
Gamma.break <- cbind(Gamma, c(1,1))

DiagDeltaT(Phi, Gamma = Gamma.break) %>% try()
```

## Gamma with one more row and one more col

```{r}
Gamma.break <- cbind(rbind(Gamma, c(1,1)), c(1,1,1))

DiagDeltaT(Phi, Gamma = Gamma.break) %>% try()
```


# xstart_DeltaT

## xstart_deltaT = 0

```{r}
xstart_deltaT.break <- 0

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
DiagDeltaT.obj
```

The output is the same

## xstart_DeltaT = 1.5

```{r}
xstart_deltaT.break <- 1.5

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
DiagDeltaT.obj
```

## xstart_DeltaT = 1500

```{r}
xstart_deltaT.break <- 1500

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
DiagDeltaT.obj
```

## xstart_DeltaT = 15

```{r}
xstart_deltaT.break <- 15

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
DiagDeltaT.obj
```

## xstart_DeltaT = 5

```{r}
xstart_deltaT.break <- 5

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
DiagDeltaT.obj
```

## xstart_DeltaT = -5

```{r}
xstart_deltaT.break <- -5

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
DiagDeltaT.obj
```

## xstart_DeltaT = "text"

```{r}
xstart_deltaT.break <- "text"

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```

## xstart_DeltaT = NA

```{r}
xstart_deltaT.break <- NA

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```

## xstart_DeltaT = NULL

```{r}
xstart_deltaT.break <- NULL

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```

## xstart_DeltaT = c(1, 2, 3)

```{r}
xstart_deltaT.break <- c(1,2,3)

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```

## xstart_DeltaT = c(4, 2, 3)

```{r}
xstart_deltaT.break <- c(4,2,3)

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```

## xstart_DeltaT = c(4, NA, 3)

```{r}
xstart_deltaT.break <- c(4,NA,3)

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```

## xstart_DeltaT = c(NA, NA, 3)

```{r}
xstart_deltaT.break <- c(NA,NA,3)

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```

## xstart_DeltaT = c(NA, NA, NA)

```{r}
xstart_deltaT.break <- c(NA,NA,NA)

DiagDeltaT(Phi, SigmaVAR, xstart_DeltaT = xstart_deltaT.break) %>% try()
```
