---
title: "Testing the input and output of MaxDeltaT"
author: "Judith Neve"
date: "20/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(CTmeta)
```

This document tests what can be used as input and output for the function Area. Each argument is examined in turn, and at the end some additional checks are done to verify plots can be made for different configurations of the model.

Where the function runs, the output is compared to the expected output.

After every attempt to "break" the function, a diagnostic is written as a comment in the code chunk, and the code chunk is followed by a "to do" list to indicate what needs to be specified/improved/changed in the function documentation or the function itself.

Original example:

```{r}
## Example 1 ##

##################################################################################################
# Input needed in examples below with q=2 variables.
# I will use the example matrices stored in the package:
DeltaT <- 1
Phi <- myPhi[1:2, 1:2]
# or: Drift
Drift <- myDrift
##################################################################################################

MaxDeltaT(DeltaT = DeltaT, Phi = Phi)
# or
MaxDeltaT(DeltaT, Phi)

# Note that the DeltaT for which Phi_ij reaches its maximum or minimum ('DeltaT_MinOrMaxPhi') differs per Phi_ij.
# Therefore, the matrix 'MinOrMaxPhi' is not a Phi-matrix, but each element should be inspected separately.
# To obtain the full Phi-matrix for a specific DeltaT one can use:
DeltaT_MinOrMaxPhi <- MaxDeltaT(DeltaT, Phi)$DeltaT_MinOrMaxPhi
StandTransPhi(DeltaTStar = DeltaT_MinOrMaxPhi[1,2], DeltaT, N = NULL, Phi)

# If you would use the drift matrix Drift as input, then use:
MaxDeltaT(DeltaT, Drift = Drift)


# Note that the function 'PhiPlot' can help to see (per element) whether a minimum or maximum is reached.
PhiPlot(DeltaT, Phi)
# or:
ggPhiPlot(DeltaT, Phi)


## Example 2: input from fitted object of class "varest" ##
#
data <- myData
if (!require("vars")) install.packages("vars")
library(vars)
out_VAR <- VAR(data, p = 1)
DeltaT <- 1
MaxDeltaT(DeltaT, out_VAR)
#
ggPhiPlot(DeltaT, out_VAR)


## Example 3: input from fitted object of class "ctsemfit" ##
#
if (!require("ctsem")) install.packages("ctsem")
library(ctsem)
library(ctsemOMX)
#
############ adapted from https://rdrr.io/cran/ctsemOMX/man/ctFit.html ############
data(ctExample1)
model <- ctModel(n.manifest=2, n.latent=2, Tpoints=6, LAMBDA=diag(2),
                manifestNames=c('LeisureTime', 'Happiness'),
                latentNames=c('LeisureTime', 'Happiness'), TRAITVAR="auto")
out_CTM <- ctFit(dat=ctExample1, ctmodelobj=model)
##################################################################################
#
MaxDeltaT(DeltaT, out_CTM)
#
ggPhiPlot(DeltaT, out_CTM)
```


# DeltaT

## DeltaT = 0

```{r}
DeltaT.broken <- 0

MaxDeltaT(DeltaT.broken, Phi) %>% try()
```

## DeltaT = -1

```{r}
DeltaT.broken <- -1

MaxDeltaT(DeltaT.broken, Phi) %>% try()
```

## DeltaT = 10

```{r}
DeltaT.broken <- 10

MaxDeltaT(DeltaT, Phi)$DeltaT_MinOrMaxPhi == MaxDeltaT(DeltaT.broken, Phi)$DeltaT_MinOrMaxPhi
MaxDeltaT(DeltaT, Phi)$MinOrMaxPhi == MaxDeltaT(DeltaT.broken, Phi)$MinOrMaxPhi
```

## DeltaT = c(1, 2)

```{r}
DeltaT.broken <- c(1, 2)

MaxDeltaT(DeltaT.broken, Phi) %>% try()
```

## DeltaT = c(0, 1)

```{r}
DeltaT.broken <- c(0, 1)

MaxDeltaT(DeltaT.broken, Phi) %>% try()
```


# Phi

## Phi with NA

```{r}
Phi.broken <- Phi
Phi.broken[1,1] <- NA

MaxDeltaT(DeltaT, Phi.broken) %>% try()
```

Problem in Phi clear enough

## Phi with text

```{r}
Phi.broken <- Phi
Phi.broken[1,1] <- "text"

MaxDeltaT(DeltaT, Phi.broken) %>% try()
```

Problem in Phi clear enough

## Phi with one more col

```{r}
Phi.broken <- cbind(Phi, c(1,1))

MaxDeltaT(DeltaT, Phi.broken) %>% try()
```

Error message works

## Phi with one more row

```{r}
Phi.broken <- rbind(Phi, c(1,1))

MaxDeltaT(DeltaT, Phi.broken) %>% try()
```

Error message works

## Phi with one more col and one more row

```{r}
Phi.broken <- matrix(c(2, -1, 0, -1, 2, -1, 0, -1, 2), nrow = 3, byrow = TRUE)

MaxDeltaT(DeltaT, Phi.broken) %>% try()
```

Runs


# Drift

## Drift with NA

```{r}
Drift.broken <- Drift
Drift.broken[1,1] <- NA

MaxDeltaT(DeltaT, Drift = Drift.broken) %>% try()
```

Error message added

## Drift with text

```{r}
Drift.broken <- Drift
Drift.broken[1,1] <- "text"

MaxDeltaT(DeltaT, Drift = Drift.broken) %>% try()
```

Error message added

## Drift with one more col

```{r}
Drift.broken <- cbind(Drift, c(1,1))

MaxDeltaT(DeltaT, Drift = Drift.broken) %>% try()
```

Correct error

## Drift with one more row

```{r}
Drift.broken <- rbind(Drift, c(1,1))

MaxDeltaT(DeltaT, Drift = Drift.broken) %>% try()
```

Correct error

## Drift with one more col and one more row

```{r}
Drift.broken <- rbind(cbind(Drift, c(1,1)), c(1,1,1))

MaxDeltaT(DeltaT, Drift = Drift.broken) %>% try()
```

Runs


# Both Phi and Drift

## Phi (broken) and Drift (working)

```{r}
Phi.broken <- Phi
Phi.broken[1,1] <- NA

MaxDeltaT(DeltaT, Phi.broken, Drift)
MaxDeltaT(DeltaT, Phi, Drift)
```

Runs :)

## Phi (working) and Drift (broken)

```{r}
Drift.broken <- Drift
Drift.broken[1,1] <- NA

MaxDeltaT(DeltaT, Phi, Drift.broken) %>% try()
```

So Drift is used by default.